Can machine learning correct microwave humidity radiances for the influence of clouds?

### 2021-01-22 Article/ici_submm_cloudcorr.tex
change AWS --> SMS

The main focus of this study is the potential of this cloud-correction
method using sub-millimetre (sub-mm) observations, which will become available
operationally with the launch of the Ice Cloud Imager \citep[ICI,][]{eriksson:towar:20} on board the next generation of European Organisation for the Exploitation of Meteorological Satellites Polar System - Second Generation (EUMETSAT EPS-SG), but will likely also be included in
several smaller missions (such as Arctic Weather Satellite (AWS); presented
below). Additionally, we demonstrate the feasibility of the approach based on
89 and 150\ GHz channels \citep[following][]{geer2015scatteringindex}, which are available on several sensors extant today. The focus
on sub-mm channels is motivated by several reasons. First, the higher
frequencies are more sensitive to scattering effects from smaller
hydrometeors and are thus expected to provide greater sensitivity to high altitude cirrus clouds. For example, in some cloudy situations the
cloud impact at 183\,GHz may be of the order of thermal noise and modelling uncertainties,
while the impact at 325\,GHz is significant enough to provide sufficient signal to noise for identifying cloud. Second, the proposed
cloud correction methods allow integration of ICI sub-mm observations in
clear-sky DA schemes with no further modifications, thus providing a simple
way to make use this novel data source as soon as it becomes available.

@@

\subsubsection{Artic Weather Satellite}
%
\begin{table}[t]
	\caption{Specifications of AWS channels relevant to this study.}
	\label{tab:specifications_AWS}	
	\begin{tabular}{lrrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
				& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		AWS-32	&	176.31    & 2000	&	0.45	\\
		AWS-33	&	178.81    & 2000 	&	0.45\\
		AWS-34	&	180.31    & 1000 	&	0.64\\
		AWS-35	&	181.51    & 1000 	&	0.64 \\
		AWS-36	&	182.31    & \phantom{0}500  &	0.88 \\
		AWS-41  & 325.15$\pm$6.60    & 2800 	 &0.60\\
		AWS-42  & 325.15$\pm$4.10    & 1800    &0.75	\\
		AWS-43  & 325.15$\pm$2.40    & 1200    &0.92\\
		AWS-44  & 325.15$\pm$1.20    & \phantom{0}800  &1.12  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The AWS is a small satellite mission suggested as an European Space Agency (ESA) Earth Watch Programme Element. It is a small platform carrying a single across-track scanning microwave radiometer. It is planned as a small but cost-effective platform, which can supplement the information from other polar orbiting satellites. The first prototype mission is expected to be delivered around 2023. The exact channels onboard AWS are not yet set, but five 183\,GHz and four 325\,GHz channels are presently planned. A brief summary of these channels is provided in Table~\ref{tab:specifications_AWS}.

In this study, forward simulations of the channels around 183\,GHz and 325\,GHz were conducted.

@@

ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator \citep[ARTS,][]{buehler:artst:18}. For the forward simulations, Cloud Satellite \citep[Cloudsat,][]{Stephens2002cloudsat} profiles during August 2015 are randomly selected. The input data are restricted between $60\unit{^{\degree}S}$ to $60\unit{^{\degree}N}$, and surface is below 500\,m. Both clear-sky and all-sky scenarios  are simulated. The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}. For ICI and AWS, 220\,000 and 143\,000 cases are simulated, respectively. All AWS sensor viewing angles (from $0^{\degree}$ to $45^{\degree}$) are simulated, but the results described in this study are based on nadir viewing angle. Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, Gaussian noise is added according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} -- Table~\ref{tab:specifications_AWS}).

The simulations are split into training and testing datasets. The training dataset is used to train the machine learning model, while the testing dataset is used to evaluate the trained model. The construction and details of the model are described in Sect.~\ref{sec:QRNN}. For MWHS-2, 220\,000 simulations are randomly selected as training dataset, while 70\,000 are used for testing. For ICI, 175\,000 cases are randomly picked to form the training set. The remaining 45\,000 are used for testing. A smaller database is selected for AWS. 120\,000 simulations are used for training and the remaining 23\,000 for testing.

@@

	\item In the second experiment, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz. This special case of utilizing only 325\,GHz channels can be relevant for smaller satellite missions like AWS where higher sub-mm channels are not available. In this experiment, QRNN-single configuration is used and it is trained with all-sky simulations from all 325\,GHz frequencies from AWS and the target 183\,GHz channel. For example, for the target AWS-32, the training inputs are AWS-32, AWS-41, AWS-42, AWS-43, AWS-44. QRNN is trained five times for each 183\,GHz channel as target. Note that for this experiment, AWS was chosen due to availability of extra 325\,GHz and 183\,GHz channels. 	
\end{enumerate}

@@

\subsubsection{AWS}

\begin{table*}[t]
	\caption{Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for AWS channels. The fraction of rejected cases is given in parentheses. }
	\label{tab:statistics_qrnn_aws}
	\begin{tabular}{llrr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
		\cline{3-6}
		&&Clear-sky &   All-sky &  \multicolumn{2}{c}{Pred.}  \\
		&&   &    &   (All) & (5\,K) \\
		\middlehline
		AWS-32  &Bias     & 0.00 &$-$1.32 &$-$0.04 &$-$0.02 (4.71\,\%) \\
				&MAE      & 0.36 &  1.57 &  0.58 &  0.44 \\
				&STD      & 0.46 &  6.42 &  1.15 &  0.64 \\
				&Skewness & 0.01 &$-$8.43 &$-$1.09 &$-$2.29 \\
		\middlehline
		AWS-33	&Bias     &  0.00 &$-$1.00 &$-$0.04 &$-$0.02 (3.75\,\%)  \\
				&MAE      &  0.36 &  1.24 &  0.46 &  0.37  \\
				&STD      &  0.45 &  5.17 &  0.87 &  0.52  \\
				&Skewness &$-$0.01 &$-$9.59 &$-$3.25 &$-$1.26  \\

		\middlehline
		AWS-34	&Bias    &  0.00 & $-$0.71 &$-$0.06 &$-$0.04 (2.86\,\%)  \\
				&MAE      &  0.50 &   1.10 &  0.47 &  0.41  \\
				&STD      &  0.63 &   4.05 &  0.82 &  0.56  \\
				&Skewness &$-$0.01 &$-$11.06 &$-$3.53 &$-$1.02  \\
		\middlehline
		AWS-35	&Bias    &$-$0.00 & $-$0.45 &$-$0.03 &$-$0.03 (1.92\%)  \\
				&MAE      &  0.50 &   0.86 &  0.48 &  0.43  \\
				&STD      &  0.63 &   2.90 &  0.77 &  0.57  \\
				&Skewness &  0.00 &$-$13.43 &$-$2.46 &$-$0.62  \\
		\middlehline
		AWS-36  &Bias    &$-$0.01 & $-$0.29 &$-$0.04 &$-$0.04 (1.23\,\%)  \\
				&MAE      &  0.71 &   0.90 &  0.63 &  0.60  \\
				&STD      &  0.89 &   2.17 &  0.88 &  0.77  \\
				&Skewness &  0.00 &$-$13.54 &$-$1.32 &$-$0.27  \\
		\bottomhline				
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}
In an analogy to the results from ICI channels, we perform a similar error distribution analysis  and the results are displayed in Table~\ref{tab:statistics_qrnn_aws}. For channel AWS-32, the average bias and standard deviation in the uncorrected dataset is $-$1.32\,K and 6.42\,K respectively. However, after correction, the bias and standard deviation reduce to $-$0.04\,K and 1.15\,K, respectively. A decrease in the skewness of error distributions is evident, but a relatively high value after correction indicates presence of cases with partially-corrected cloud impact. Filtering out cases with 5\,K correction improves the statistics but introduces asymmetry in the error distribution. This is most likely due to rejection of cases affected by over-estimation. For AWS-33, the predictions have slightly higher accuracy than AWS-32. The MAE in predictions is only 0.46\,K in comparison to 1.24\,K for the all-sky simulations. High skewness despite low bias (0.04\,K) is most likely due to presence of isolated cases with large negative deviations. Nonetheless, filtering such cases makes the distribution more symmetric. For AWS-34 and AWS-35, again a similar behaviour is seen, though the distributions are more symmetric in the latter. For AWS-36, we obtain the most symmetric and narrow distributions after correction owing to the low sensitivity of AWS-36 to hydrometeor impact.  Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of prediction errors is narrower than noise for AWS-34, AWS-35 and AWS-36.

@@

\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/fig12.pdf}	
	\caption{The average confidence intervals ($\pm3\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
	\label{fig:uncertainty_cloud_impact}	
\end{figure}
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/fig13.pdf}	
	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-single for channels I1V, I2V and I3V.}
	\label{fig:error_distribution_uncertainty_bins}	
\end{figure*}
%f

@@

With AWS, the behaviour of predicted uncertainties is observed to be similar as for ICI (not shown). However, the relation between the mean uncertainty estimate ($\pm3\sigma$) and cloud impact is displayed in Fig.~\ref{fig:uncertainty_cloud_impact}. For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness. As fraction of cloud impact increases, the predictions become increasingly uncertain. The most uncertain predictions are for the lowest peaking channel AWS-32, which incidentally is also most affected by  hydrometeor impact.

To conclude the results, we analyse if the uncertainty estimates given by QRNN are representative of prediction accuracy. Figure~\ref{fig:error_distribution_uncertainty_bins} shows the observed ICI errors binned by their corresponding uncertainty in $\pm\,2\sigma$  confidence interval. For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the prediction increases. The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm\,$2.5\,K. With increase in the uncertainty, frequency of cases with high accuracy decreases and the distributions spread out symmetrically to higher errors. Poor predictions occur more frequently when uncertainty is high. Cases with accurate predictions yet high uncertainty are also present. In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties follow the same relationship. Similar results are also obtained with AWS (not shown).

@@

A similar pattern is seen when only one 325\,GHz channel is used to correct cloud impact in AWS. QRNN is successful in predicting NFCS values for all channels except for the lowest peaking channel AWS-32. For AWS-32, the resulting error distributions have significantly lower spread than the all-sky simulations, but are still negatively skewed. In spite of the slightly inferior performance for AWS-32, the high accuracy for other channels indicates that a single sub-mm channel like 325\,GHz is also sufficient for cloud correction at 183\,GHz. This is an important result as smaller satellites may be limited by their size to measure several sub-mm wavelengths.

With ICI and AWS, for some channels the variability of errors smaller than measurement noise is achieved. This is a consequence of predictions for cases which lack cloud impact. QRNN predictions are weighted mean of measurements between channels. In the absence of clouds, also the sub-mm channels provide humidity information that is incorporated in the 183 GHz NFCS estimate and some compensation of noise can be achieved. This effect is observed to be stronger in ICI than AWS, as the former has a higher number of channels giving redundant information. Note that with actual satellite measurements, the spread of error distributions smaller than sensor noise could be difficult to achieve due to other underlying uncertainties not considered here.

@@

Based on the promising results from MWHS-2, and with future scope, we extend the study to include data from Ice Cloud Imager (ICI) sub-millimetre (sub-mm) channels. The results show that with  sub-mm channels, QRNN is able to correctly predict most of the cloudy cases and can provide high quality cloud corrected radiances. The predicted radiances have symmetric and narrow error distributions and for some channels the spread is smaller than the measurement noise. This makes it highly suitable for application to data assimilation (DA) systems. The robustness of sub-mm channels in cloud correction is also demonstrated with use of only 325\,GHz for cloud correction. This is applicable to smaller satellite missions like AWS, where only one of the higher frequencies is available. The results indicate that utilisation of only 325\,GHz can also be beneficial when other channels are absent. It's possible that the ICI sub-mm channels could also be used to cloud correct humidity radiances from MicroWave Imager (MWI)---another conically scanning radiometer onboard Metop-SG. MWI will measure frequencies from 18\,GHz to 183\,GHz. Both MWI and ICI have the same requirements for incidence angle and fore-view observations, but different footprints. Although re-mapping to a common footprint  would slightly compromise the data quality, the high accuracy achieved with ICI simulations suggests that the QRNN would work well even when actual measurements are available.

@@

\appendix
\section{ARTS setup}    %% Appendix A
\label{appendix:ARTS_setup}
%
All radiative transfer forward simulations are made by the Atmospheric Radiative
Transfer System \citep[ARTS,][]{eriksson:arts2:11,buehler:artst:18}), version
arts-2.3.1. All simulations are based on dBZ-based model system presented by \citet{ekelund2020using}, i.e.\ CloudSat reflectivities are used as input and are converted to ice water content (IWC) and rain water content (RWC) using microphysical assumptions. For each atmospheric case, both all-sky and clear-sky calculations are performed. In the former, all hydrometeors contents are set to zero, while in the latter, IWC and RWC derived from CloudSat reflectivities, and liquid water content (LWC) from ERA-Interim \citep{dee2011erainterim} are included. In order to avoid a possible bias between clear-sky and all-sky calculations for insignificant hydrometeor contents, both calculations are made by the RT4 solver \citep{evans1995microwavec}. The absorption model takes into account the effect from nitrogen
\citep{pwr:93}, oxygen \citep{pwr:93}, liquid water content \citep[LWC,][]{ellison2007permittivity}, and water vapour. For water vapour, absorption model as  in RTTOV \citep[Radiative transfer for TOVS,][]{saunders2018update} is followed, but with few modifications \citep{turner2019amsutran}. LWC is assumed to be totally absorbing. In the mapping of CloudSat reflectivities to RWC and IWC, a total separation between liquid and ice phase is assumed. All scattering hydrometeors at temperatures above 0$^{\degree}$C and below 0$^{\degree}$\,C are assumed to be rain and ice hydrometeors, respectively. For RWC the particle size distribution (PSD) of \citet{abel2012improved} is applied. The PSD of IWC follows the basic formulation applied in DARDAR \citep[\url{
	http://www.icare.univ-lille1.fr/projects/dardar}][]{delanoe2008variational}, using latest parameter values (i.e.\ $\alpha$ and $\beta$) as given by \citet{cazenave2019evolution}.
This PSD can be considered as a ``two moment'' scheme, but is here applied in
a one moment manner by setting $N_0^*$ (as a function of temperature)
following Table~5 of \citet{delanoe2014normalized}, and letting the radar
reflectivity set the remaining moment. Single scattering data are taken from
\citet{eriksson:agene:18}. For ice hydrometeors, three habits are applied:
perpendicular 3-bullet rosette, large plate aggregate and large column
aggregate. In the last two cases, the aggregates are complemented with single
crystal data to also cover smaller sizes. These data describe particles
assumed to have a totally random orientation. To apply oriented particles is
much more computationally costly and could not be accommodated inside the
study. The land emissivity was taken from Tool to Estimate Land‐Surface Emissivities at Microwave frequencies \citep[TELSEM,][]{aires2011tool} and the
Ocean/water from Tool to Estimate Sea‐Surface Emissivity from Microwaves to sub‐Millimeter waves \citep[TESSEM,][]{prigent2017sea}.

Using the setup described above, forward simulations are performed for ICI and AWS. The output from ARTS is first two elements of the Stokes vector,  which are converted to brightness temperatures for H- and V-polarisation.

@@

Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for both ICI and AWS QRNN experiments. However, for MWHS-2, an identical hyper-parameter framework but three hidden layers gave best results.

@@

\begin{acknowledgements}
The part associated with AWS was done with funding from EUMETSAT (contract  EUM/CO/20/4600002417/CJA), while remaining work was mainly funded by the Swedish National Space Agency (grants 166/18 and 154/19). David Duncan is supported by the EUMETSAT Fellowship Programme.
This project would not had been possible without the contribution of all individuals behind the open source softwares used (ARTS, Python, PyTorch, Numpy and Matplotlib).
\end{acknowledgements}

>>>>

The main focus of this study is the potential of this cloud-correction
method using sub-millimetre (sub-mm) observations, which will become available
operationally with the launch of the Ice Cloud Imager \citep[ICI,][]{eriksson:towar:20} on board the next generation of European Organisation for the Exploitation of Meteorological Satellites Polar System - Second Generation (EUMETSAT EPS-SG). Additionally, we demonstrate the feasibility of the approach based on 89 and 150\ GHz channels \citep[following][]{geer2015scatteringindex}, which are available on several sensors extant today. The focus
on sub-mm channels is motivated by several reasons. First, the higher
frequencies are more sensitive to scattering effects from smaller
hydrometeors and are thus expected to provide greater sensitivity to high altitude cirrus clouds. For example, in some cloudy situations the
cloud impact at 183\,GHz may be of the order of thermal noise and modelling uncertainties,
while the impact at 325\,GHz is significant enough to provide sufficient signal to noise for identifying cloud. Second, the proposed
cloud correction methods allow integration of ICI sub-mm observations in
clear-sky DA schemes with no further modifications, thus providing a simple
way to make use this novel data source as soon as it becomes available.

@@

\subsubsection{Small Microwave Satellite}
%
\begin{table}[t]
	\caption{Specifications of SMS channels.}
	\label{tab:specifications_SMS}	
	\begin{tabular}{lrrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
				& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		SMS-1	&	176.31    & 2000	&	0.45	\\
		SMS-2	&	178.81    & 2000 	&	0.45\\
		SMS-3	&	180.31    & 1000 	&	0.64\\
		SMS-4	&	181.51    & 1000 	&	0.64 \\
		SMS-5	&	182.31    & \phantom{0}500  &	0.88 \\
		SMS-6  & 325.15$\pm$6.60    & 2800 	 &0.60\\
		SMS-7  & 325.15$\pm$4.10    & 1800    &0.75	\\
		SMS-8  & 325.15$\pm$2.40    & 1200    &0.92\\
		SMS-9  & 325.15$\pm$1.20    & \phantom{0}800  &1.12  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The Small Microwave Satellite (SMS) is a hypothetical satellite which we consider to represent the type of sensors currently being considered for future missions. We assume it to be a single across-track scanning microwave radiometer with five 183\,GHz channels and four 325\,GHz channels. A brief summary of the  channel specifications assumed is provided in Table~\ref{tab:specifications_SMS}.

@@

ICI and SMS frequencies are simulated with Atmospheric Radiative Transfer Simulator \citep[ARTS,][]{buehler:artst:18}. For the forward simulations, Cloud Satellite \citep[Cloudsat,][]{Stephens2002cloudsat} profiles during August 2015 are randomly selected. The input data are restricted between $60\unit{^{\degree}S}$ to $60\unit{^{\degree}N}$, and surface is below 500\,m. Both clear-sky and all-sky scenarios  are simulated. The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}. For ICI and SMS, 220\,000 and 143\,000 cases are simulated, respectively. For SMS, sensor viewing angles from $0\unit{^{\degree}S}$ to $45\unit{^{\degree}N}$ are simulated, but the results described in this study are based on nadir viewing angle. Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, Gaussian noise is added according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} -- Table~\ref{tab:specifications_SMS}).

The simulations are split into training and testing datasets. The training dataset is used to train the machine learning model, while the testing dataset is used to evaluate the trained model. The construction and details of the model are described in Sect.~\ref{sec:QRNN}. For MWHS-2, 220\,000 simulations are randomly selected as training dataset, while 70\,000 are used for testing. For ICI, 175\,000 cases are randomly picked to form the training set. The remaining 45\,000 are used for testing. A smaller database is selected for SMS. 120\,000 simulations are used for training and the remaining 23\,000 for testing.

@@

	\item In the second experiment, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz. This special case of utilizing only 325\,GHz channels can be relevant for smaller satellite missions, as represented by SMS, where higher sub-mm channels are not available. In this experiment, QRNN-single configuration is used and it is trained with all-sky simulations from all 325\,GHz frequencies from SMS and the target 183\,GHz channel. For example, for the target SMS-1, the training inputs are SMS-1, SMS-6, SMS-7, SMS-8, SMS-9. QRNN is trained five times for each 183\,GHz channel as target.

\end{enumerate}

@@

\subsubsection{SMS}

\begin{table*}[t]
	\caption{Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for SMS channels. The fraction of rejected cases is given in parentheses. }
	\label{tab:statistics_qrnn_sms}
	\begin{tabular}{llrr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
		\cline{3-6}
		&&Clear-sky &   All-sky &  \multicolumn{2}{c}{Pred.}  \\
		&&   &    &   (All) & (5\,K) \\
		\middlehline
		SMS-1  &Bias     & 0.00 &$-$1.32 &$-$0.04 &$-$0.02 (4.71\,\%) \\
				&MAE      & 0.36 &  1.57 &  0.58 &  0.44 \\
				&STD      & 0.46 &  6.42 &  1.15 &  0.64 \\
				&Skewness & 0.01 &$-$8.43 &$-$1.09 &$-$2.29 \\
		\middlehline
		SMS-2	&Bias     &  0.00 &$-$1.00 &$-$0.04 &$-$0.02 (3.75\,\%)  \\
				&MAE      &  0.36 &  1.24 &  0.46 &  0.37  \\
				&STD      &  0.45 &  5.17 &  0.87 &  0.52  \\
				&Skewness &$-$0.01 &$-$9.59 &$-$3.25 &$-$1.26  \\

		\middlehline
		SMS-3	&Bias    &  0.00 & $-$0.71 &$-$0.06 &$-$0.04 (2.86\,\%)  \\
				&MAE      &  0.50 &   1.10 &  0.47 &  0.41  \\
				&STD      &  0.63 &   4.05 &  0.82 &  0.56  \\
				&Skewness &$-$0.01 &$-$11.06 &$-$3.53 &$-$1.02  \\
		\middlehline
		SMS-4	&Bias    &$-$0.00 & $-$0.45 &$-$0.03 &$-$0.03 (1.92\%)  \\
				&MAE      &  0.50 &   0.86 &  0.48 &  0.43  \\
				&STD      &  0.63 &   2.90 &  0.77 &  0.57  \\
				&Skewness &  0.00 &$-$13.43 &$-$2.46 &$-$0.62  \\
		\middlehline
		SMS-5  &Bias    &$-$0.01 & $-$0.29 &$-$0.04 &$-$0.04 (1.23\,\%)  \\
				&MAE      &  0.71 &   0.90 &  0.63 &  0.60  \\
				&STD      &  0.89 &   2.17 &  0.88 &  0.77  \\
				&Skewness &  0.00 &$-$13.54 &$-$1.32 &$-$0.27  \\
		\bottomhline				
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}
In an analogy to the results from ICI channels, we perform a similar error distribution analysis  and the results are displayed in Table~\ref{tab:statistics_qrnn_sms}. For channel SMS-1, the average bias and standard deviation in the uncorrected dataset is $-$1.32\,K and 6.42\,K respectively. However, after correction, the bias and standard deviation reduce to $-$0.04\,K and 1.15\,K, respectively. A decrease in the skewness of error distributions is evident, but a relatively high value after correction indicates presence of cases with partially-corrected cloud impact. Filtering out cases with 5\,K correction improves the statistics but introduces asymmetry in the error distribution. This is most likely due to rejection of cases affected by over-estimation. For SMS-2, the predictions have slightly higher accuracy than SMS-1. The MAE in predictions is only 0.46\,K in comparison to 1.24\,K for the all-sky simulations. High skewness despite low bias (0.04\,K) is most likely due to presence of isolated cases with large negative deviations. Nonetheless, filtering such cases makes the distribution more symmetric. For SMS-3 and SMS-4, again a similar behaviour is seen, though the distributions are more symmetric in the latter. For SMS-5, we obtain the most symmetric and narrow distributions after correction owing to the low sensitivity of SMS-5 to hydrometeor impact.  Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of prediction errors is narrower than noise for SMS-3, SMS-4 and SMS-5.

@@

\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/fig12.pdf}	
	\caption{The average confidence intervals ($\pm3\sigma$) plotted against the magnitude of cloud impact for all SMS channels.}
	\label{fig:uncertainty_cloud_impact}	
\end{figure}
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/fig13.pdf}	
	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-single for channels I1V, I2V and I3V.}
	\label{fig:error_distribution_uncertainty_bins}	
\end{figure*}
%f

@@

With SMS, the behaviour of predicted uncertainties is observed to be similar as for ICI (not shown). However, the relation between the mean uncertainty estimate ($\pm3\sigma$) and cloud impact is displayed in Fig.~\ref{fig:uncertainty_cloud_impact}. For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness. As fraction of cloud impact increases, the predictions become increasingly uncertain. The most uncertain predictions are for the lowest peaking channel SMS-1, which incidentally is also most affected by  hydrometeor impact.

To conclude the results, we analyse if the uncertainty estimates given by QRNN are representative of prediction accuracy. Figure~\ref{fig:error_distribution_uncertainty_bins} shows the observed ICI errors binned by their corresponding uncertainty in $\pm\,2\sigma$  confidence interval. For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the prediction increases. The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm\,$2.5\,K. With increase in the uncertainty, frequency of cases with high accuracy decreases and the distributions spread out symmetrically to higher errors. Poor predictions occur more frequently when uncertainty is high. Cases with accurate predictions yet high uncertainty are also present. In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties follow the same relationship. Similar results are also obtained with SMS (not shown).

@@

A similar pattern is seen when only one 325\,GHz channel is used to correct cloud impact in SMS. QRNN is successful in predicting NFCS values for all channels except for the lowest peaking channel SMS-1. For SMS-1, the resulting error distributions have significantly lower spread than the all-sky simulations, but are still negatively skewed. In spite of the slightly inferior performance for SMS-1, the high accuracy for other channels indicates that a single sub-mm channel like 325\,GHz is also sufficient for cloud correction at 183\,GHz. This is an important result as smaller satellites may be limited by their size to measure several sub-mm wavelengths.

With ICI and SMS, for some channels the variability of errors smaller than measurement noise is achieved. This is a consequence of predictions for cases which lack cloud impact. QRNN predictions are weighted mean of measurements between channels. In the absence of clouds, also the sub-mm channels provide humidity information that is incorporated in the 183 GHz NFCS estimate and some compensation of noise can be achieved. This effect is observed to be stronger in ICI than SMS, as the former has a higher number of channels giving redundant information. Note that with actual satellite measurements, the spread of error distributions smaller than sensor noise could be difficult to achieve due to other underlying uncertainties not considered here.

@@

Based on the promising results from MWHS-2, and with future scope, we extend the study to include data from Ice Cloud Imager (ICI) sub-millimetre (sub-mm) channels. The results show that with  sub-mm channels, QRNN is able to correctly predict most of the cloudy cases and can provide high quality cloud corrected radiances. The predicted radiances have symmetric and narrow error distributions and for some channels the spread is smaller than the measurement noise. This makes it highly suitable for application to data assimilation (DA) systems. The robustness of sub-mm channels in cloud correction is also demonstrated with use of only 325\,GHz for cloud correction. This is applicable to smaller satellite missions as represented by SMS, where only one of the higher frequencies is available. The results indicate that utilisation of only 325\,GHz can also be beneficial when other channels are absent. It's possible that the ICI sub-mm channels could also be used to cloud correct humidity radiances from MicroWave Imager (MWI)---another conically scanning radiometer onboard Metop-SG. MWI will measure frequencies from 18\,GHz to 183\,GHz. Both MWI and ICI have the same requirements for incidence angle and fore-view observations, but different footprints. Although re-mapping to a common footprint  would slightly compromise the data quality, the high accuracy achieved with ICI simulations suggests that the QRNN would work well even when actual measurements are available.

@@

\appendix
\section{ARTS setup}    %% Appendix A
\label{appendix:ARTS_setup}
%
All radiative transfer forward simulations are made by the Atmospheric Radiative
Transfer System \citep[ARTS,][]{eriksson:arts2:11,buehler:artst:18}), version
arts-2.3.1. All simulations are based on dBZ-based model system presented by \citet{ekelund2020using}, i.e.\ CloudSat reflectivities are used as input and are converted to ice water content (IWC) and rain water content (RWC) using microphysical assumptions. For each atmospheric case, both all-sky and clear-sky calculations are performed. In the former, all hydrometeors contents are set to zero, while in the latter, IWC and RWC derived from CloudSat reflectivities, and liquid water content (LWC) from ERA-Interim \citep{dee2011erainterim} are included. In order to avoid a possible bias between clear-sky and all-sky calculations for insignificant hydrometeor contents, both calculations are made by the RT4 solver \citep{evans1995microwavec}. The absorption model takes into account the effect from nitrogen
\citep{pwr:93}, oxygen \citep{pwr:93}, liquid water content \citep[LWC,][]{ellison2007permittivity}, and water vapour. For water vapour, absorption model as  in RTTOV \citep[Radiative transfer for TOVS,][]{saunders2018update} is followed, but with few modifications \citep{turner2019amsutran}. LWC is assumed to be totally absorbing. In the mapping of CloudSat reflectivities to RWC and IWC, a total separation between liquid and ice phase is assumed. All scattering hydrometeors at temperatures above 0$^{\degree}$C  and below 0$^{\degree}$\,C are assumed to be rain and ice hydrometeors respectively. For RWC, the particle size distribution (PSD) of \citet{abel2012improved} is applied. The PSD of IWC follows the basic formulation applied in DARDAR \citep[\url{
	http://www.icare.univ-lille1.fr/projects/dardar}][]{delanoe2008variational}, using latest parameter values (i.e.\ $\alpha$ and $\beta$) as given by \citet{cazenave2019evolution}.
This PSD can be considered as a ``two moment'' scheme, but is here applied in a one moment manner by setting $N_0^*$ (as a function of temperature)
following Table~5 of \citet{delanoe2014normalized}, and letting the radar reflectivity set the remaining moment. Single scattering data are taken from
\citet{eriksson:agene:18}. For ice hydrometeors, three habits are applied:
perpendicular 3-bullet rosette, large plate aggregate and large column
aggregate. In the last two cases, the aggregates are complemented with single crystal data to also cover smaller sizes. The particles are assumed to have a totally random orientation. 
To apply oriented particles is much more computationally costly and could not be accommodated inside the study. The land emissivity was taken from Tool to Estimate Land‐Surface Emissivities at Microwave frequencies \citep[TELSEM,][]{aires2011tool} and the
Ocean/water from Tool to Estimate Sea‐Surface Emissivity from Microwaves to sub‐Millimeter waves \citep[TESSEM,][]{prigent2017sea}.

Using the setup described above, forward simulations are performed for ICI and SMS. The output from ARTS is first two elements of the Stokes vector,  which are converted to brightness temperatures for H- and V-polarisation.

@@

Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for both ICI and SMS QRNN experiments. However, for MWHS-2, an identical hyper-parameter framework but three hidden layers gave best results.

@@

\begin{acknowledgements}
The part associated with SMS was done with funding from EUMETSAT (contract  EUM/CO/20/4600002417/CJA), while remaining work was mainly funded by the Swedish National Space Agency (grants 166/18 and 154/19). David Duncan is supported by the EUMETSAT Fellowship Programme.
This project would not had been possible without the contribution of all individuals behind the open source softwares used (ARTS, Python, PyTorch, Numpy and Matplotlib).
\end{acknowledgements}
